Supervised Learning Notes

### 2017-08-10 cheatsheets/modelvalidation_cheatsheet.Rmd
univariate analysis on training data

* vtreat::kWayCrossValidation(nRows, nSplits, dframe, y)
    + nrows: number of rows to be split
    + nSplits: desired number of cross-validation folds
    + can set other two arguments to null (aren't used for kWayCrossVal but for compatibility with vtreat)
* Cross-validation predicts how well a model built from all the data will perform on new data. As with the test/train split, for a good modeling procedure, cross-validation performance and training performance should be close
* if the estimated model performance looks good enough, then fit a final model with all of the data (performance between cv and full model should be similar), can't evaluate final model's future performance since there is no data to do so
    + cross validation validates the MODELING PROCESS, not the actual model (test/train split does test how the model will perform on future data)

@@

# for(i in 1:k) {
  # Get the ith split
  # split <- splitPlan[[i]]
  # Build a model on the training data from this split (lm, in this case)
  # model <- lm(fmla, data = dframe[split$train,])
  # make predictions on the application data from this split
  # dframe$pred.cv[split$app] <- predict(model, newdata = dframe[split$app,])
}

>>>>

* vtreat::kWayCrossValidation(nRows, nSplits, dframe, y)
    + nrows: number of rows to be split
    + nSplits: desired number of cross-validation folds
    + can set other two arguments to null (aren't used for kWayCrossVal but for compatibility with vtreat)
* Cross-validation predicts how well a model built from all the data will perform on new data. As with the test/train split, for a good modeling procedure, cross-validation performance and training performance should be close
* all predictions from CV are essentially test set predictions- so RMSE and r-square calculated from these predictions should give an unbiased estimate of how a model fit to all the training data will perform on future data 
if the estimated model performance looks good enough, then fit a final model with all of the data (performance between cv and full model should be similar), can't evaluate final model's future performance since there is no data to do so
    + cross validation validates the MODELING PROCESS, not the actual model (test/train split does test how the model will perform on future data)

@@

# for(i in 1:k) {
  # Get the ith split
  # split <- splitPlan[[i]]
  # Build a model on the training data from this split (lm, in this case)
  # model <- lm(fmla, data = dframe[split$train,])
  # make predictions on the application data from this split
  # dframe$pred.cv[split$app] <- predict(model, newdata = dframe[split$app,])
#}
